--- 
title: "Project proposal"
author: "Passionate Puffins"
output: html_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readxl)
```

## 1. Introduction

Our data set is: Androscoggin County High school detailed tables on surveyed questions high schoolers were asked. 
Question: How healthy are kids in the Androscoggin County High School?

1. We are viewing how many times in the past year (12 months) have you been drunk or high in school. Percentage of students who. have answered at least one time. 

1. Categorizing total percentage of students by age

2. Categorizing a graph by gender 

3. Making a graph of ethnicity

4.Data of "Have good parents to talk to" vs. the data of amount of times high or drunk in school

5. Data of high/drunk y vs. If you wanted to get marijuana how easy would it be

6.Had drugs sold to them on school property vs. Data of high/drunk 



## 2. Data

```{r}
Growth_data <- read_xlsx("../data/How many times in the past year (12 months) have you been drunk or high at school? (hn126) Percentage of students who answered at least 1 time.xlsx")
```



```{r}
view (Growth_data)
```


## 3. Data analysis plan

Text goes here.


```{r}
# Code goes here
```


## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

