--- 
title: "Project proposal"
author: "Passionate Puffins"
output: html_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(readxl)
```

## 1. Introduction

Our data set is: Androscoggin County High school detailed tables on surveyed questions high schoolers were asked. 
Question: How healthy are kids in the Androscoggin County High School?

1. We are viewing how many times in the past year (12 months) have you been drunk or high in school. Percentage of students who. have answered at least one time. 

1. Categorizing total percentage of students by age

2. Categorizing a graph by gender 

3. Making a graph of ethnicity

4.Data of "Have good parents to talk to" vs. the data of amount of times high or drunk in school

5. Data of high/drunk y vs. If you wanted to get marijuana how easy would it be

6.Had drugs sold to them on school property vs. Data of high/drunk 



## 2. Data

```{r rename-variables}
Growth_data <- read_xlsx("../data/How many times in the past year (12 months) have you been drunk or high at school? (hn126) Percentage of students who answered at least 1 time.xlsx")


```


```{r rename varaible}

Growth_data <- Growth_data %>%
  rename("Percent Total Age" = "Percent Total Ague")
         
```

```{r View Data }
view (Growth_data)
```

```{r Glimpse of The Data}
glimpse(Growth_data)
```
```{r}
dim(Growth_data) 
```


Our data set is 10x9 with 10 different variables and 70 observations that we are going to be able to incorporate into visualizations. There is no code book for the data set as I had to manually input all of the data into an excel sheet as the format we were given the data was not suitable to use in r. I am in the process of incorporating more data into our set that will allow us to gain additional insight into potentially what the cause is for these students showing up drunk or high to school is. We have categorical variables as well as discrete numerical variables within our set. As I add more data to the set we will be able to include continuous numerical variables which will allow us to see a range of percentages for variables.  


## 3. Data analysis plan

Text goes here.


```{r}
# Code goes here
```


## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

