---
title: "Project proposal"
author: "Passionate Puffins"
output: html_document
---

```{r load-packages, message = FALSE}
#install.packages("tidyverse")
library(tidyverse)
library(broom)
```

## 1. Introduction

Text goes here. Refer to the Markdown Quick Reference: Help -> Markdown Quick Reference. 

## 2. Data

Text goes here.

```{r}
Growth_data <- read_xlsx("../data/How many times in the past year (12 months) have you been drunk or high at school? (hn126) Percentage of students who answered at least 1 time.xlsx")
```

```{r}
view (Growth_data)
```

## 3. Data analysis plan

Based on our research question, "How big a role do systems of support (through school or family) play in the health of Androscoggin youth?", we plan to compare various indications of good support systems against indications of unhealthy youth behavior. For example, we plan to create a visualization and analysis to contrast how much a child feels supported by their parents against how easy it would be for them to attain drugs. How effective is a good support system (how much the child feels supported by their parents) in preventing unhealthy behavior (buying/using drugs)? 

We will likely use a bar graph similar to the one below to visualize the patterns between the data.   


```{r}
# Code goes here
```


## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

