--- 
title: "Project proposal"
author: "Passionate Puffins"
output: html_document
---

```{r load-packages, message = FALSE}
#install.packages("tidyverse")
library(tidyverse)
library(broom)
library(readxl)
```

## 1. Introduction

Our data comes from Androscoggin County High school. They surveyed their students about drug use, alcohol consumption, smoking habits, eating habits, home lives, and how much support they felt they were recieving from their parents. We will be using this data to evaluate the health of students at Androscoggin County High school compared to how much support they feel they are recieving from their parents.  

Research Question: How big a role do home support systems play in the health of Androscoggin youth? 

## 2. Data

```{r}
Growth_data <- read_xlsx("../data/How many times in the past year (12 months) have you been drunk or high at school? (hn126) Percentage of students who answered at least 1 time.xlsx")
```



```{r}
view (Growth_data)
```


## 3. Data analysis plan

Based on our research question, we plan to compare various indications of good support systems against indications of unhealthy youth behavior. For example, we plan to create a visualization and analysis to contrast how much a child feels supported by their parents against how easy it would be for them to attain drugs. How effective is a good familial support system (how much the student feels supported by their parents) in preventing unhealthy behavior (buying/using drugs)? 

To answer the question effectively, we will create multiple visualizations similar to this, including:

- How many times in the past year (12 months) have you been drunk or high in school (percentage of students who answered one time or more)? vs. Students who answered 'Very or often' or 'Extremely or almost always' to 'I have parents who are good at talking with me about things.' 

- During the past 30 days, on how many days did you smoke cigars, cigarillos, or little cigars (percentage of students who answered 'at least one day')? vs. Students who answered 'Very or often' or 'Extremely or almost always' to 'I have parents who are good at talking with me about things.' 

We plan to categorize and consider variables within the datasets such as race and gender. We will likely use a bar graph similar to the one below to visualize the patterns between the data.   


```{r}
# Code goes here
```


## 4. Data Ethics Review

The data ethics review section will be introduced in a separate class and is not part of the original proposal deadline.

