---
title: "Project memo"
author: "Team name"
output: github_document
---

This document should contain a detailed account of the data clean up for your data and the design choices you are making for your plots. For instance you will want to document choices you've made that were intentional for your graphic, e.g. color you've chosen for the plot. Think of this document as a code script someone can follow to reproduce the data cleaning steps and graphics in your handout.

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)

```

## Data Clean Up Steps for Overall Data

### Step 1: Load and clean all data

```{r}
kids_overweight <- read_csv("/cloud/project/data/kids_overweight.csv")

family_support_data <- read.csv ("/cloud/project/data/love_support_family.csv")

drinking_vs_family <- read.csv ("/cloud/project/data/drinking_fam_GRADE.csv")

Drinking_vs_family <- drinking_vs_family |>
  mutate(
    Grade = fct_recode(Grade, 
                       NULL = "")
  )


```

### Step 2: ________

## Plots

### Plot 1: Grade vs. Drinking data

#### Data cleanup steps specific to plot 1

```{r data-cleanup-plot-1}
Drinking_data_cleaner <- read.csv("../data/drunk_high_data_2.csv")
#Drinking_vs_family <- Drinking_vs_family |> 
 # as.numeric(GradePercent)
#Drinking_vs_family <- Drinking_vs_family |>
 # as.numeric(FamGradePer.)
```


#### Final Plot 1

```{r plot-1-visualization}
Drinking_vs_family |>
  mutate('Grade' = fct_relevel(Grade,
                               "Grade 9", 
                               "Grade 10", 
                               "Grade 11", 
                               "Grade 12"), 
         GradePercent = as.numeric(gsub("%", "", GradePercent))) |>
  filter(!is.na(Grade) & !is.na(`GradePercent`)) |>
  ggplot(aes(x = Grade, y = `GradePercent`, fill = Grade)) +
  geom_col(na.rm = TRUE) +
  scale_y_continuous(breaks = seq(0, 20, by = 5),
                     labels = scales::label_percent(scale = 1)) + 
  labs(x = NULL, 
       y = 'Percentage', 
       title = 'How many times in the past year have you been drunk/high at school?', 
       subtitle = "Grade vs. Percentage of Students Who Answered 'At Least One Time'")+
  theme_classic()

ggsave("../plots/plot-1.jpg", width = 10, height = 4)
```


### Plot 2: Family support at home vs. Drinking Data

#### Plot 2 Cleanup

```{r}

family_support_data <- read.csv ("/cloud/project/data/love_support_family.csv")
drinking_vs_family <- read.csv ("/cloud/project/data/drinking_fam_GRADE.csv")

Drinking_vs_family <- drinking_vs_family |>
  mutate(
    Grade = fct_recode(Grade, 
                       NULL = "")
  )
```


#### Final Plot 2

```{r plot-2-visualization}
Drinking_vs_family |>
  mutate('Grade' = fct_relevel(Grade,
                               "Grade 9", 
                               "Grade 10", 
                               "Grade 11", 
                               "Grade 12"), 
         GradePercent = as.numeric(gsub("%", "", GradePercent)),
         FamGradePer. = as.numeric(gsub("%", "", FamGradePer.))) |>
  filter(!is.na(Grade) & !is.na(`GradePercent`)) |>
  pivot_longer(
    cols = c(GradePercent, FamGradePer.),
    names_to = "Metric",
    values_to = "Percent") |>
  mutate(Metric = recode(Metric,
                       GradePercent = "Been Drunk/High at School",
                       `FamGradePer.` = "Felt Supported by Family")) |>
  ggplot(aes(x = Grade, y = `Percent`, fill = Metric)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_y_continuous(breaks = seq(0, 100, by = 10),
                     labels = scales::label_percent(scale = 1)) +
  labs(x = NULL, 
       y = 'Percentage', 
       title = 'Family support vs. being drunk or high at school by grade') +
  theme_classic()
  
ggsave("../plots/plot-2.jpg", width = 10, height = 4)
```

### Plot 3: Percentage of overweight kids categorized by age

```{r}
kids_overweight |>
  ggplot(aes(x=Age, 
             y=Percentage, 
             fill = Age)) +
  geom_col() + 
  labs(title = "Percentage of Kids Overweight by Age Group", 
       x = "Age", 
       y = "Percentage of Kids Overweight") +
  theme_classic()

```

### Plot 4: ___________ 

