---
title: "Project memo"
author: "Team name"
output: github_document
---

This document should contain a detailed account of the data clean up for your data and the design choices you are making for your plots. For instance you will want to document choices you've made that were intentional for your graphic, e.g. color you've chosen for the plot. Think of this document as a code script someone can follow to reproduce the data cleaning steps and graphics in your handout.

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)

```

## Data Clean Up Steps for Overall Data

### Step 1: _________

```{r}
kids_overweight <- read_csv("/cloud/project/data/kids_overweight.csv")

```

### Step 2: ________

## Plots

### ggsave example for saving plots

```{r starwars ggsave example}
p1 <- starwars |>
  filter(mass < 1000, 
         species %in% c("Human", "Cerean", "Pau'an", "Droid", "Gungan")) |>
  ggplot() +
  geom_point(aes(x = mass, 
                 y = height, 
                 color = species)) +
  labs(x = "Weight (kg)", 
       y = "Height (m)",
       color = "Species",
       title = "Weight and Height of Select Starwars Species",
       caption = paste("This data comes from the starwars api: https://swapi.py43.com"))


ggsave("example-starwars.png", width = 4, height = 4)

ggsave("example-starwars-wide.png", width = 6, height = 4)
```

# WORK ON THISSSS!!!
```{r}
#ggplot(kids_overweight, aes(x=Age, y=Percentage)) +
#  geom_bar()

```

```


### Plot 1: Grade vs. Drinking data

#### Data cleanup steps specific to plot 1

These data cleaning sections are optional and depend on if you have some data cleaning steps specific to a particular plot

```{r data-cleanup-plot-1}
Drinking_data_cleaner <- read.csv("../data/drunk_high_data_2.csv")
```


#### Final Plot 1

```{r plot-1-visualization}
Drinking_vs_family |>
  mutate('Grade' = fct_relevel(Grade,
                               "Grade 9", 
                               "Grade 10", 
                               "Grade 11", 
                               "Grade 12")) |>
  filter(!is.na(Grade) & !is.na(`GradePercent`)) |>
  ggplot(aes(x = Grade, y = `GradePercent`, fill = Grade)) +
  geom_col(na.rm = TRUE) +
  labs(x = NULL, 
       y = 'Percentage', 
       title = 'How many times in the past year have you been drunk/high at school?', 
       subtitle = "Grade vs. Percentage of Students Who Answered 'At Least One Time'")+
  theme_classic()

ggsave("../plots/plot-1.jpg", width = 10, height = 4)
```


### Plot 2: Family support at home vs. Drinking Data

#### Plot 2 Cleanup

```{r}

family_support_data <- read.csv ("/cloud/project/data/love_support_family.csv")
drinking_vs_family <- read.csv ("/cloud/project/data/drinking_fam_GRADE.csv")

Drinking_vs_family <- drinking_vs_family |>
  mutate(
    Grade = fct_recode(Grade, 
                       NULL = "")
  )
```


#### Final Plot 2

```{r plot-2-visualization}
Drinking_vs_family |>
  mutate('Grade' = fct_relevel(Grade,
                               "Grade 9", 
                               "Grade 10", 
                               "Grade 11", 
                               "Grade 12"), 
         FamGradePer. = as.factor(FamGradePer.)
         )|>
  filter(!is.na(Grade) & !is.na(`GradePercent`)) |>
  ggplot(aes(x = Grade, y = `GradePercent`, fill = FamGradePer.)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = NULL, 
       y = 'Percentage', 
       title = 'Family support vs. being drunk or high at school by grade')+
  theme_classic()
ggsave("../plots/plot-2.jpg", width = 10, height = 4)
```

### Plot 3: ___________

Add more plot sections as needed. Each project should have at least 3 plots, but talk to me if you have fewer than 3.

### Plot 4: ___________ 

